%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gregory Mitchell} \\ \vspace{1pt}
    \small 613-207-3865 $|$ \href{mailto:grmitch1@gmail.com}{\underline{grmitch1@gmail.com}} $|$ 
    \href{https://linkedin.com/in/gregmitch}{\underline{linkedin.com/in/gregmitch}} $|$
    \href{https://github.com/GregMitch}{\underline{github.com/GregMitch}}
\end{center}


%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages \& Databases}{: Rust, C/C++, Python, Java, JavaScript, PostgreSQL, Cosmos DB} \\
      \textbf{Developer Tools}{: Git, Docker, Jenkins, WinDbg, AWS Lambda, Amazon EC2, Jira} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{Jan 2023 -- Present}
      {Trend Micro}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed a Windows registry scanner for the Integrity Monitor rewrite as part of the \href{https://www.trendmicro.com/en_ca/business/products/hybrid-cloud/deep-security.html}{\underline{Deep Security}} product.}
        \resumeItem{Enhanced Jenkins infrastructure to increase the maximum product version limit by 100\% and support hotfixes.}
        \resumeItem{Initiated porting C++ features to Rust \& presented training material accessible to 7000+ employees globally.}
        \resumeItem{Implemented database migration so users can seamlessly upgrade from the legacy version to the latest.}
        \resumeItem{Resolved customer-reported issues with the legacy Log Inspection module and provided timely solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer CO-OP}{May. 2022 -- Aug 2022}
      {Trend Micro}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Implemented rule metrics in the Application Control feature resulting in faster diagnosis for customer issues.}
        \resumeItem{Patched a PowerShell vulnerability by parsing scripts and ensuring only pre-authorized scripts are executed.}
        \resumeItem{Optimized \& enhanced wildcard matching algorithm with dynamic programming to include globstar support.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Tester CO-OP}{May 2021 -- Aug 2021}
      {Nokia}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Created automated test suites in JavaScript with Selenium \& Mocha to verify \href{https://www.nokia.com/networks/ip-networks/network-services-platform/}{\underline{web application}} functionality.}
        \resumeItem{Updated legacy automation test suites to maintain a success rate of greater than 95\%.}
        \resumeItem{Utilized XML scripts to modify user permissions and network nodes, decreasing configuration time by 50\%.}
      \resumeItemListEnd

      \resumeSubheading
      {Automation Engineer CO-OP}{Sept 2020 -- Dec 2020}
      {Nokia}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Designed automated TCL scripts to test router MACsec functionalities to comply with the 802.1AE standard.}
        \resumeItem{Maintained Nokia-Cisco-Juniper MACsec interoperability tests, ensuring compatibility between routers.}
        \resumeItem{Verified bug fixes in customer environments and raised a ticket when new issues were found.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Side Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Member Engagement Lead} $|$ \emph{Python, CSV, Git, Discord, Reverse Engineeing}}{Google Developer Student Club}
          \resumeItemListStart
            \resumeItem{Organized and moderated community events on Discord to engage members and host networking events.}
            \resumeItem{Co-hosted a \href{https://www.youtube.com/watch?v=CBb6tFfmoBI}{\underline{cyber-security workshop}} explaining different types of malware and common attacks.}
            \resumeItem{Made a \href{https://github.com/GregMitch/Attendance-Checker}{\underline{CSV pasrer}} with Python to determine who attended the most events and distributed prizes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/The-Homiesexuals/imghost/commits/master?author=GregMitch}{\underline{Imghost}}} $|$ \emph{Python, Flask, sqlite3, Amazon S3, Git}}{uOttaHack2021}
          \resumeItemListStart
            \resumeItem{Developed a website to host, share and tag user-uploaded images with team at uOttaHack2021.}
            \resumeItem{Implemented backend routing using Python Flask to handle HTTP requests, returning formatted JSONs.}
            \resumeItem{Generated readable random phrases with Python for use as image ids that pointed to internal image links.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


 %-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Ottawa}{Ottawa, ON}
    {Bachelor of Applied Science in Software Engineering: 3.7 GPA}{Sept. 2018 -- Jan 2023}
\resumeSubHeadingListEnd
\resumeItemListStart
  \resumeItem{Admissions Scholarship: \$3000}
  \resumeItem{Data Structures \& Algorithms, Software Architecture, Quality Assurance, Software Requirements, Databases, Computer Architecture, Computer Networks, Object Oriented Programming}
\resumeItemListEnd

%-------------------------------------------
\end{document}